Detection of eco-evolutionary dynamics in metacommunities using Joint Species Distribution Models

### 2023-06-14 manuscript/manuscript_v04.Rmd
Moved mscript, added res file, began res walkthrough

---
title: "Detection of eco-evolutionary dynamics in metacommunities using Joint Species Distribution Models"
author: "Jelena H. Pantel, Ruben Hermann"
date: Ecological Modelling, Faculty of Biology, University of Duisburg-Essen, Universitätsstraße 5, 45141 Essen, Germany
output:
  pdf_document: default
  bookdown::pdf_document2: default
  html_document: default
  word_document:
    reference_docx: docx_template.docx
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Pantel, JH}
- \fancyhead[R]{Detection of ecoevo dynamics}
- \usepackage{lineno}
- \linenumbers
linestretch: 2
link-citations: yes
linkcolor: blue
csl: evolution.csl
bibliography: refs.bib
---

>>>>

---
title: "Detection of eco-evolutionary dynamics in metacommunities using Joint Species Distribution Models"
author: "Jelena H. Pantel, Ruben Hermann"
date: Ecological Modelling, Faculty of Biology, University of Duisburg-Essen, Universitätsstraße 5, 45141 Essen, Germany
output:
  bookdown::pdf_document2: default
  html_document: default
  word_document:
    reference_docx: docx_template.docx
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Pantel, JH}
- \fancyhead[R]{Detection of ecoevo dynamics}
- \usepackage{lineno}
- \linenumbers
linestretch: 2
link-citations: yes
linkcolor: blue
csl: evolution.csl
bibliography: refs.bib
---
